Compilation with Dynamic Grammars

### 2017-04-23 papers/paper.tex
Adds FORTRAN functions/interfaces

A transformer file is just a series of these transformations:
\begin{verbatim}
createreg [name]
// Copy an element from global multisymbol table to a key in a register's multisymbol table
reg [name] transfer(-append) [reg-key] [global-key]
// Move the multisymbol from a register to the destination key in the multisymbol table. If a destination_reg is specified, this table is the table of a register. Otherwise, it is the global multisymbol table
pushback [reg-name] [destination] (optional)[destination_reg]
// Prefix for performing an operation on a register
reg [name] {command (any of below)}

>>>>

A transformer file is just a series of these transformations:
\begin{verbatim}
createreg [name]
// Copy an element from global multisymbol table to a key in a register's multisymbol table
transfer(-append) [reg-name] [global-key] [reg-key] 
// Move the multisymbol from a register to the destination key in the multisymbol table. If a destination_reg is specified, this table is the table of a register. Otherwise, it is the global multisymbol table
pushback(-override) [reg-name] [destination] (optional)[destination_reg]
// Prefix for performing an operation on a register
reg [name] {command (any of below)}
